---
title: "The Pima, Framingham, datasets"
author: "Valentine Tagbo"
date: "2/18/2020"
output: html_document
---


```{r}
#1.This dataset contains studies conducted on pima American Indians from the state of Arizona.
#The dataset contain 9 numeric integer variables and 769 observations.
#The most interesting thing that I found about the Pima dataset that was originally obtained from 
#the National Institute of Diabetes and Digestive and Kidney Diseases was that the subjects that 
#observed were of the same ethnicity and their diets seem to be virtuallly identicle.

#2.The difficulty that might arise as a result of analyzing this dataset is that one cannot certainly 
#narrow the cause of diabetes amoung pima perople to a single variable. There might be more than
#one variable in concert with each other that could potentially contribute to the diagnosis of 
#diabetes among this group.

#3. QUESTION: What is the major predictor of diabetes among the pima people from the 9 variables under study?

df_pimadiabetes <- read.csv('pima_diabetes.csv', header=TRUE)
str(df_pimadiabetes)
head(df_pimadiabetes)
```
```{r}
summary(df_pimadiabetes)

```

```{r}
# The scatter plot of Crude.Birth.Rate as a function of Year

plot(df_pimadiabetes$Glucose, 
     df_pimadiabetes$Pregnancies,
     xlab = "Glucose",
     ylab = "Number of Pregnacies",
     col = "blue",
     main = "Graph of Pregnacies as a Function of Glucose")


plot(df_pimadiabetes$Glucose, 
     df_pimadiabetes$BloodPressure,
     xlab = "Glucose",
     ylab = "Blood Presure",
     col = "green",
     main = "Graph of Blood Pressure as a Function of Glucose")


plot(df_pimadiabetes$Glucose, 
     df_pimadiabetes$BMI,
     xlab = "Glucose",
     ylab = "Body Mass Index",
     col = "red",
     main = "Graph of BMI as a Function of Glucose")
```

##########################################################################################################################################################################################################################

```{r}
###The framingham dataset dontain 16 numeric/integer variables and 4240 observations. The dataset
###contain some missing values represented with NA's. The dataset also contain categorical variable 
####and continuous varibles.
###What I found to be very intriguing is that the study span a period of 3 generations after 
###original cohorts recruited in Framingham, MA. The researchers focussed on the leading cause of
###death in the United States till date.

#####Question: What are the factors that are mostly corrlated to increased risk of Cardiovascular diseases.

df_framingham <- read.csv('framingham.csv', header=TRUE)
str(df_framingham)
head(df_framingham)
summary(df_framingham)
df_framingham$male[df_framingham$male==0]<-"female"
df_framingham$male[df_framingham$male==1]<-"male"


count <- table(df_framingham$male)
barplot(count,col= "cyan")


hist(df_framingham$age,
      main='The Histogram of Age',
      xlab = 'Age when the Subjects Were First Examined',
      ylab = 'Frequency',
      breaks=5,
      col="lightgreen",
      border="darkgreen")

boxplot(df_framingham$BMI ~ df_framingham$cigsPerDay,
     xlab = "Number of Cigarettes Smoked Per Day",
     ylab = "Body Mass Index",
     col = "red",
     main = "Graph of BMI as a Function of Cigarattes")



